Relational Parametricity for Algebraically Indexed Types

### 2012-05-29 paper/section-general-framework.tex
Fix definition of simultaneous substitution composition
Fix some working

The \emph{composition} of two simultaneous substitutions $\sigma :
\Delta \Rightarrow \Delta'$ and $\sigma' : \Delta' \Rightarrow \Delta$
is defined as $(\sigma^*e'_1, ..., \sigma^*e'_n)$, where $\sigma' =
(e'_1,...,e'_n)$.

@@

Since the definition of the index-erasure interpretation has
completely ignored the indexing, and type equality is defined as an
extension of index equality, it is straightforward to prove that equal
types have equal denotations when interpreted in the index-erasure
semantics, and that substitution of index terms has no effect on the
index-erasure interpretation of types:
\begin{lemma}\label{lem:tyeqsubst-erasure}
  \begin{enumerate}
  \item If $\Delta \vdash A \equiv B \isType$ then $\tySem{A} =
    \tySem{B}$; and
  \item If $\Delta \vdash A \isType$ and $\sigma : \Delta' \Rightarrow
    \Delta$, then $\tySem{\sigma^*A} = \tySem{A}$.
  \end{enumerate}
\end{lemma}

>>>>

The \emph{composition} of two simultaneous substitutions $\sigma :
\Delta \Rightarrow \Delta'$ and $\sigma' : \Delta' \Rightarrow
\Delta''$, where $\sigma' = (e'_1,...,e'_n)$, is defined as $\sigma'
\circ \sigma \isDefinedAs (\sigma^*e'_1, ..., \sigma^*e'_n) : \Delta
\Rightarrow \Delta''$.

@@

Since the index-erasure interpretation has completely ignores the
index expressions and type equality is defined as an extension of
index equality, it is straightforward to prove that equal types have
equal denotations when interpreted in the index-erasure semantics, and
that substitution of index terms has no effect on the index-erasure
interpretation of types:
\begin{lemma}\label{lem:tyeqsubst-erasure}
  \begin{enumerate}
  \item If $\Delta \vdash A \equiv B \isType$ then $\tySem{A} =
    \tySem{B}$; and
  \item If $\Delta \vdash A \isType$ and $\sigma : \Delta' \Rightarrow
    \Delta$, then $\tySem{\sigma^*A} = \tySem{A}$.
  \end{enumerate}
\end{lemma}
